This section is meant to be an abstract-like description of your position to provide context for panel members. \\

Provide a concise, summary-level, introductory statement describing your current position’s purpose and your research environment, including the scope of the research you conduct (for example, topical, geographic, taxonomic), your primary collaborators, and your major sources (but not amounts) of funding.
Include relevant information about your typical role on research teams (for example, principal investigator, team leader, or team member).\\

As applicable, document other major assignments or responsibilities, such as standing representation or committee assignments and any non-research duties. 
Include the percentage of time spent on these duties.
This may include, for example: 

\begin{itemize}
\item technical assistance related to an assignment, committee assignments, technology transfer, or consultation;
\item facility or laboratory management;
\item special assignments (for example, safety officer responsibilities); or
\item substantive supervisory duties.
\end{itemize}

This should describe the duties of your position, but not include outcomes or accomplishments.
Detailed lists of projects, examples of accomplishments, and other specifics are better included in the following sections.
Do not include information about your physical work environment. \\

This section is limited to 2,500 characters, including spaces (about three-quarters of a page).
If this section exceeds the character limit, your Scientist Record may be returned to you for editing, which may delay your grade evaluation.
