\subsection{Professional and Scientific Service}

\begin{enumerate}


\item Scientific review panels and workshops 
  \begin{itemize}
  \item \textbf{Workshop 1},
    April 2014 \\
    Venue.
    City.\\
    Briefly describe if needed.
  \end{itemize}
  
\item Editorial boards

  \begin{itemize}
  \item \textbf{Editorial Board Member}, Journal 1.  2016--Present
  \item \textbf{Reviewing Editor}, Journal 2.
    2019--2021\label{ERed}
  \item \textbf{Associate Editor}, Journal 3, 2023--present\label{jfwm}
  \end{itemize}

\item Society Service 

  \begin{itemize}
  \item Example committee 1 (2015--present)
  \item Example committee 2 (2010--present)
  \end{itemize}

\item Conference planning

  \begin{itemize}
  \item Assisted in organizing Meeting 2014
  \item Assisted in organizing Meeting 2024
  \end{itemize}
  
\item \textbf{Journal referee.} I typically review 1--3 journal
  articles per month.
  Most recent reviews are summarized on my Web of Science (previously
  Publons) Profile
  (\url{https://www.webofscience.com/wos/author/record/1122397}).
  I have reviewed for the following journals (listed
  alphabetically):\\
  \textit{A journal},
  \textit{B journal},
  and the \textit{C journal}.
\end{enumerate}

\subsection{Academic Service}\label{acSer}

\subsubsection*{Academic appointments}

\begin{itemize}
\item Adjunct Professor (Courtesy Appointment, no rank),
University of State, Department of Awesomeness (2014-Present)
\end{itemize}

\subsection*{Students or postdocs advised or mentored}\label{mentor}

\begin{itemize}
\item Jane Done.
  MS graduate committee member.
  State University.
  Fall 2024--present.
\item Dr.~John Doe.
  Postdoc.
  Co-mentored with Jane Smith.
  University of State.
  Fall 2023--Present.
\item Sarah Student,
  Research Intern.
  State School.
  June 2021--September 2022.
  Next position: Acme Inc.
\end{itemize}
 
\subsubsection*{Courses taught and seminars presented}

\begin{enumerate}
\item A course at National Meeting. Location. January 2007.
\item Cool research talk.
Weekly seminar.
Department of Awesomeness.
State University.
April 2008.
 
  \noindent\makebox[\linewidth]{\rule{\textwidth}{1pt}} 
  \textbf{Start of USGS service}
  
\item Example talk.
    
  \noindent\makebox[\linewidth]{\rule{\textwidth}{1pt}}
  \textbf{Review and promotion: 2017 RGE Panel} 
  
\item Another workshop. 

  \noindent\makebox[\linewidth]{\rule{\textwidth}{1pt}}
  \textbf{Last review and promotion: 2021 RGE Panel} 

\item newer workshop

\item Guest lecture.
\end{enumerate}

\subsection{Technical Training Provided}\label{TTP}

\begin{enumerate}
\item Smith JD and \textbf{Powell JW}. Training course of rafting. North American Rafting Meeting. Colorado River, CO. Full-day course. November 1881.

  \noindent\makebox[\linewidth]{\rule{\textwidth}{1pt}} 
  \textbf{Start of USGS service}

\item example item

  \noindent\makebox[\linewidth]{\rule{\textwidth}{1pt}} 
  \textbf{Review and promotion: 2017 RGE Panel} 

\item example item.
  \noindent\makebox[\linewidth]{\rule{\textwidth}{1pt}} 
  \textbf{Last review: 2021 RGE Panel} 

\item example 
   
\end{enumerate}

\subsection{Other mentorship}\label{mentor:other}

\begin{itemize}
\item Dr.~Jane Doe,
  Faculty on sabbatical learning about occupancy modeling and applied
  Bayesian statistics.
  Also, I assisted Dr.~Doe is using USGS data for teaching and
  education outreaching including high-school students, college
  students, graduate students, and continuing education for middle and
  high school teachers.
  State school.
  Fall 2019.
 
\end{itemize}

