\subsection{Awards and Recognition}

\begin{itemize}
\item Award 1.
\item Award 2.
  
\end{itemize}


\subsection{Special Assignments}

None.

\subsection{Inventions and Patents}

None.

\subsection{Outreach and Media Coverage}

\begin{enumerate}
\item Outreach
  \begin{itemize}
  \item Example 1.
  \end{itemize}
  
\item Media coverage\label{sec:TITD}

  \begin{itemize}
  \item Example 1
  \end{itemize}
\end{enumerate}

\subsection{Previous Professional Positions}

Overview if needed.
Otherwise, list positions.

\begin{itemize}
\item \textit{Geologist (GS-0482-11) \hfill January 1877--April 1878}
\item \textit{Adventurer (GS-0401-11)  	 \hfill June 1878--January
    1881} 
\end{itemize}


\subsection{Education}

\begin{itemize}
\item University, \textit{Doctorate of Philosophy}, August 2013\\
Major: Rocks, Minor: Botany
\item  University, \textit{Masters of Science}, August 2009\\
Major: Rocks
\item University of State, \textit{Bachelors of Science}, May 2007\\
Majors:Rocks and Water, Minor: Fish
\end{itemize}


\subsubsection*{\small{Privacy Act Notice:}}
\vspace{-0.3cm}
\begin{adjustwidth}{0cm}{}
  {\footnotesize
Pursuant to Section 3(e)(3) of the Privacy Act of 1974 (Public Law
93-573), the individual furnishing information on this form is hereby
advised as follows: 1. The authority for solicitation of the
information is 5 USC 552(a). 2. The principal purpose for which the
information is intended to be used is for the U.S. Geological Survey
research and development peer panel review process. 3. The routine
disclosure of the information is to scientific, management and
administrative staff who are participants in the peer review process
or who are in the human resources office. 4. The effect on the
individual of not providing all or any part of the requested
information is not having an up-to-date Research and Development
Scientific Record for peer review thereby resulting in a delayed or no
peer review. 5. This record and information in this record may be used
by the Federal government in connection with the hiring of an
employee, the issuance of a security clearance, the conducting of a
security or suitability investigation of an individual, the
classifying of jobs, the letting of a contract, and the issuance of a
license, grant, or other benefits or awards to the extent that the
information is relevant and necessary.
}
\end{adjustwidth}
